---
title: "Assign2"
author: "Eunhee Lee"
date: "May 11, 2017"
output:
  html_document: default
  word_document: default
---


###1-1.Read the gazetteer data as-is into a gaz_raw tibble a


```{r eval=TRUE, echo=TRUE, warning=FALSE}
ca <- read.delim("../wrangle/data/CA_Features_20170401.txt", header=TRUE, sep="|",na="")
```



###1-2.Copy only the following columns into a gaz tibble 

```{r eval=TRUE, echo=TRUE, warning=FALSE}
colnames(ca)[1] <- "FEATURE_ID" # change the first column name
library(tidyverse)
ca <- select(ca,FEATURE_ID,FEATURE_NAME, FEATURE_CLASS, STATE_ALPHA, COUNTY_NAME, PRIM_LAT_DEC, PRIM_LONG_DEC, SOURCE_LAT_DEC, SOURCE_LONG_DEC, ELEV_IN_M, MAP_NAME, DATE_CREATED, DATE_EDITED)
```



###1-3.Convert the gaz columns to the appropriate type
####(Convert any placeholders for unknown data to NA - this process has been done in the first step.)

```{r eval=TRUE, echo=TRUE, warning=FALSE}
ca <- as_tibble(ca) 

```



###1-4.Delete from gaz rows where: 
####a) the primary latitude or longitude are unknown, b) the feature is not in California

```{r eval=TRUE, echo=TRUE, warning=FALSE}
ca <-ca[!(is.na(ca$PRIM_LAT_DEC)) | !(is.na(ca$PRIM_LONG_DEC)),]
ca <- filter(ca, STATE_ALPHA == "CA")
write.table(ca,"CAdata.csv", sep = "|")
``` 

###2-1 What is the most-frequently-occuring feature name?

```{r eval=TRUE, echo=TRUE, warning=FALSE}
Analysis1 <- group_by(ca,FEATURE_CLASS)
AnalyFre <- summarise(Analysis1, count=n())
leastclass=which.min(AnalyFre$count)
AnalyFre[leastclass,c("FEATURE_CLASS","count")]
```



###2-2.What is the least-frequently-occuring feature class?

```{r eval=TRUE, echo=TRUE, warning=FALSE}
Analysis2 <- group_by(ca,FEATURE_NAME)
AnalyFre2 <- summarise(Analysis2, count=n())
mostname=which.max(AnalyFre2$count)
AnalyFre2[mostname,c("FEATURE_NAME","count")]
```



###2-3.What is the approximate center point of each county? 

```{r eval=TRUE, echo=TRUE, warning=FALSE}
Analysis3a <- group_by(ca,COUNTY_NAME)%>% 
  summarise(Centercounty = mean(PRIM_LONG_DEC, na.rm=TRUE)) 
colnames(Analysis3a)[2] <- "MEAN_LONG_DEC"
Analysis3b <- group_by(ca,COUNTY_NAME)%>% 
  summarise(Centercounty = mean(PRIM_LAT_DEC, na.rm=TRUE)) 
colnames(Analysis3b)[2] <- "MEAN_LAT_DEC"
Analysis3 <- left_join(Analysis3a, Analysis3b)
Analysis3
```



###2-4.What are the fractions of the total number of features in each county?



```{r eval=TRUE, echo=TRUE, warning=FALSE}
Featureclass <-read.table("Featureclass.csv", header=TRUE, sep=",")
colnames(Featureclass) = c("FEATURE_CLASS", "CHARACTERISTIC")
Featureclass <- as_tibble(Featureclass)
caF <- merge(ca, Featureclass, by="FEATURE_CLASS")
Analysis4a <- group_by(caF, COUNTY_NAME)
Analysis4 <- summarise(Analysis4a,Naturalfraction = nrow(subset(Analysis4a, CHARACTERISTIC == "Natural"))/nrow(Analysis4a)*100,
            Manmadefraction = nrow(subset(Analysis4a, CHARACTERISTIC == "Manmade"))/nrow(Analysis4a)*100)  

Analysis4

```

